### 2017-10-23 paper/sections/3_posix_overheads.tex
paper: add last graph
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% what is durability
While durability is not specified by POSIX IO, users expect that files they create
or modify survive failures.  We define three types of durability: global,
local, and none.  Global
durability means that the client or server can fail at any time and metadata
will not be lost. Local durability means that metadata can be lost if the
client or server stays down after a failure. None means that metadata is volatile
and that the system provides no guarantees when clients or servers fail. 
None is different than local durability because regardless of the type failure,
metadata will be lost when components die in a None configuration.\\

% - sequential IO, trim redundant operations
\noindent\textbf{CephFS Design}: a journal of metadata updates that streams into
the resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to grow to large which
ensures (1) sequential writes into the object store and (2) the ability for daemons to
trim redundant or irrelevant journal entries.  The journal is striped over
objects where multiple journal updates can reside on the same object. There are
two tunables for controlling the journal: the segment size and the number of
parallel segments that can be written in parallel. Unless the journal saturates 
memory or CPU resources, larger values for these tunables results in better
performance.

@@

% Effects on performance
Figure~\ref{fig:overhead-a} shows the
effect of journaling of different journal segment sizes; the larger the segment
size the bigger that the writes into the object store are. The trade-off for
better performance is memory consumption because larger segments take up
more space for buffering. When journaling is on, 
the metadata server periodically stops serving requests to flush ({\it i.e.}
apply journal updates) to the metadata store.  The journal overhead is
sufficient enough to slow down metadata throughput but not so much as to
overwhelm the bandwidth of the object store. We measured our peak bandwidth to
be 100MB/s, which is the speed of our network link.\\

\noindent\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS,
to the best of our knowledge, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an SSTable) then those batched
metadata operations are lost. For DeltaFS, if the client fails then, on restart,
the computation does the work again -- since the snapshots of the namespace are
never globally consistent and there is no ground truth.  On the server side,
BatchFS and DeltaFS use IndexFS. IndexFS writes metadata to SSTables, which
initially reside in memory but are later flushed to the underlying
distributed file system.

@@

Access to metadata in a POSIX IO-compliant file system is strongly consistent, so
reads and writes to the same inode or directory are globally ordered.  The
synchronization and serialization machinery needed to ensure that all clients
see the same state has high overhead.\\

\noindent\textbf{CephFS Design}: capabilities keep metadata strongly
consistent. To reduce the number of RPCs needed for consistency, clients can
obtain capabilities for reading, creating and updating inodes, as well as caching reads,
buffering writes, changing the file size, and performing lazy IO.

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:overhead-b}.  If only one client is creating files in a
directory (``isolated" curve on \(y1\) axis) then that client can lookup the
existence of new files locally before issuing a create request to the metadata
server. If another client starts creating files in the same directory
(``interfere" curve on \(y1\) axis) then the directory inode transitions out of
read caching and the first client must send \texttt{lookup()}s to the metadata
server (``interfere" curve on \(y2\) axis). These extra requests increase the
throughput of the ``interfere" curve because the metadata server can handle the
extra load but performance suffers.  This degradation is shown in
Figure~\ref{fig:overhead-c}, where we scale the number of clients and show the
slowdown of the slowest client.  The results are normalized to a single
isolated client without a metadata server journal.  For the ``interfere" bars,
each client creates files in private directories and at 30 seconds we launch
another process that creates files in those directories. 18 clients is the
maximum number the metadata server could handle for this metadata-intensive
workload; at higher client load, the metadata server started complaining about
laggy and unresponsive requests.\\

@@

\noindent\textbf{Comparison to decoupled namespaces}: Decoupled namespaces
merge batches of metadata operations into the global namespaces when the job
completes.  In BatchFS the merge is delayed by the application using an API to
switch between asynchronous to synchronous mode. The merge itself is explicitly
managed by the application but future work looks at more automated
methodologies. In DeltaFS snapshots of the metadata subtrees stays on the client
machines; there is no ground truth and consistent namespaces are constructed
and resolved at application read time or when a 3rd party system ({\it e.g.},
middleware, scheduler, etc.) needs a view of the metadata. As a result, all the
overheads of maintaining consistency that we showed above are delayed until the
merge phase.

>>>>

% what is durability
While durability is not specified by POSIX IO, users expect that files they create
or modify survive failures.  We define three types of durability: global,
local, and none.  Global
durability means that the client or server can fail at any time and metadata
will not be lost. Local durability means that metadata can be lost if the
client or server stays down after a failure. None means that metadata is volatile
and that the system provides no guarantees when clients or servers fail. 
None is different than local durability because regardless of the type failure,
metadata will be lost when components die in a None configuration.

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: a journal of metadata updates that streams into
the resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to grow to large which
ensures (1) sequential writes into the object store and (2) the ability for daemons to
trim redundant or irrelevant journal entries.  The journal is striped over
objects where multiple journal updates can reside on the same object. There are
two tunables for controlling the journal: the segment size and the number of
parallel segments that can be written in parallel. Unless the journal saturates 
memory or CPU resources, larger values for these tunables results in better
performance.

@@

% Effects on performance
Figure~\ref{fig:overhead-a} shows the
effect of journaling of different journal segment sizes; the larger the segment
size the bigger that the writes into the object store are. The trade-off for
better performance is memory consumption because larger segments take up
more space for buffering. When journaling is on, 
the metadata server periodically stops serving requests to flush ({\it i.e.}
apply journal updates) to the metadata store.  The journal overhead is
sufficient enough to slow down metadata throughput but not so much as to
overwhelm the bandwidth of the object store. We measured our peak bandwidth to
be 100MB/s, which is the speed of our network link.

\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS,
to the best of our knowledge, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an SSTable) then those batched
metadata operations are lost. For DeltaFS, if the client fails then, on restart,
the computation does the work again -- since the snapshots of the namespace are
never globally consistent and there is no ground truth.  On the server side,
BatchFS and DeltaFS use IndexFS. IndexFS writes metadata to SSTables, which
initially reside in memory but are later flushed to the underlying
distributed file system.

@@

Access to metadata in a POSIX IO-compliant file system is strongly consistent, so
reads and writes to the same inode or directory are globally ordered.  The
synchronization and serialization machinery needed to ensure that all clients
see the same state has high overhead.

\textbf{CephFS Design}: capabilities keep metadata strongly
consistent. To reduce the number of RPCs needed for consistency, clients can
obtain capabilities for reading, creating and updating inodes, as well as caching reads,
buffering writes, changing the file size, and performing lazy IO.

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:overhead-b}.  If only one client is creating files in a
directory (``isolated" curve on \(y1\) axis) then that client can lookup the
existence of new files locally before issuing a create request to the metadata
server. If another client starts creating files in the same directory
(``interfere" curve on \(y1\) axis) then the directory inode transitions out of
read caching and the first client must send \texttt{lookup()}s to the metadata
server (``interfere" curve on \(y2\) axis). These extra requests increase the
throughput of the ``interfere" curve because the metadata server can handle the
extra load but performance suffers.  This degradation is shown in
Figure~\ref{fig:overhead-c}, where we scale the number of clients and show the
slowdown of the slowest client.  The results are normalized to a single
isolated client without a metadata server journal.  For the ``interfere" bars,
each client creates files in private directories and at 30 seconds we launch
another process that creates files in those directories. 18 clients is the
maximum number the metadata server could handle for this metadata-intensive
workload; at higher client load, the metadata server started complaining about
laggy and unresponsive requests.

@@

\textbf{Comparison to decoupled namespaces}: Decoupled namespaces
merge batches of metadata operations into the global namespaces when the job
completes.  In BatchFS the merge is delayed by the application using an API to
switch between asynchronous to synchronous mode. The merge itself is explicitly
managed by the application but future work looks at more automated
methodologies. In DeltaFS snapshots of the metadata subtrees stays on the client
machines; there is no ground truth and consistent namespaces are constructed
and resolved at application read time or when a 3rd party system ({\it e.g.},
middleware, scheduler, etc.) needs a view of the metadata. As a result, all the
overheads of maintaining consistency that we showed above are delayed until the
merge phase.

### 2017-10-23 paper/sections/6_results.tex
paper: add last graph
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{Use Case 1} \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{Use Case 2}
      \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{Use Case 3}
      \label{fig:slowdown-sync}
  \end{subfigure}
  \caption{The performance and features of Cudele. (a) shows the performance of
merging client journals at the metadata server. Performance is better than RPCs
because there are less messages and consistency/durability code paths are
bypassed. (b) shows how the allow/block API can isolate directories from
interfering clients.  (c) shows the slowdown of a single client periodically
syncing updates to the gobal namespace. The inflection point is the trade-off
of frequent updates vs. larger journal files.\label{fig:use-cases}}
\end{figure*}

>>>>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{Use Case 1} \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{Use Case 2}
      \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{Use Case 3}
      \label{fig:slowdown-sync}
  \end{subfigure}
\caption{The performance and features of Cudele. (a) shows the cost of
merging client journals at the metadata server. Merging is better than RPCs
because there are less messages and consistency/durability code paths are
bypassed. In (b), the allow/block API isolates directories from interfering
clients. (c) is the slowdown of a single client syncing updates to the gobal
namespace. The inflection point is the trade-off of frequent updates vs. larger
journal files.\label{fig:use-cases}}
\end{figure*}
